Two-Dimensional Hydrodynamics of a Janus Particle Vesicle

### 2022-03-21 doc/JFM2022/Final/main_jfm.tex
final product

\begin{figure}
\begin{center}
\includegraphics[width=\textwidth]{Figure0_Wrapper.pdf}
\end{center}
\caption{Panel (a) illustrates the domain and boundary conditions for
  the mobility problem. The color map in panels (b)--(e) is the solution
  $u$ of \eqref{eq:SL}. Red is for $\ReviewerTwo{\eta} = 1$ and blue is for $\ReviewerTwo{\eta} = 0$.
  Particles self-assemble into vesicle bilayers (panel (b)) and
  eventually arrange along inner and outer leaflets. In panel (c), $C_M$
  is the midplane curve, \ReviewerOne{and} $A$ is the enclosed area\ReviewerOne{.}
  %, and $L$ is the arc length. 
  Initially stretched vesicles relax to equilibrium with fluid
  flow across the bilayer. The study considers a single vesicle in
  background flows such as shear flow (panel (d)) and hydrodynamic
  vesicle-vesicle interactions (panel (e)).}
\label{fig:figure0}
\end{figure}

@@

In the present work, we extend the hybrid continuum model in~\cite{Fu20}
for the Janus suspension to incorporate the collective hydrodynamics of
a Janus suspension under various flows. The JP vesicles in our
simulations replicate  \ReviewerOne{well-known} vesicle hydrodynamics
such as tank-treading and inter-leaflet slippage in a shear flow and
migration in Poiseuille flow from continuum models. Furthermore we use
the hybrid continuum model to investigate permeability and rupture of a
bilayer membrane due to an imposed flow.  Finally, we compare a pair of
interacting JP vesicles with a continuum model of a pair of vesicles.

@@

To simulate the hydrodynamics of Janus particles in Stokes flow,
we require a numerical method to avoid unphysical contact between rigid
Janus particles. Optimization-based contact methods introduce
constraints, such as enforcing a non-positive space-time interference
volume (\cite{lu-rah-zor2017, Lukas19, yan-cor-mal-vee-she2020}). These
methods do not introduce stiffness, but do require solving potentially
expensive nonlinear complementarity problems at each time step.
Repulsion-based contact methods, which we employ, introduce an
artificial repulsion force that increases in strength as two particles
approach one another (\cite{glo-pan-hes-jos-per2001, fen-mic2004,
kab-qua-bir2018}). Strong repulsion forces can introduce numerical
stiffness, but with the presence of the hydrophobic forces, we maintain
contact-free suspensions with a relatively \textcolor{red}{soft} repulsive
force \textcolor{red}{(compared to the short-range repulsion that diverges in the Lennard-Jones potential)}.

@@

\section{Governing Equations\label{sec:governing_eqs}}
\subsection{\label{mobility}Mobility Problem}
The objective of this work is to study the hydrodynamics of JP vesicles
in background flows. We consider an $N_b$-many body collection of JP
suspended in a two-dimensional unbounded domain $\Omega$. The boundary
of each particle is denoted by $\Gamma_i$ so that $\bd \Omega = \Gamma_1
\cup \Gamma_2 \cup \cdots \cup \Gamma_{N_b}$ (Figure
\ref{fig:figure0}a). Assuming the inertial terms are negligible, the
governing equations are
\begin{alignat}{3}
\label{eq:stokes}
  -\mu \Delta \uu + \nabla p &= \mathbf{0}, 
    && \xx \in \Omega, \\
  \nabla\cdot \uu &= 0, \qquad && \xx \in \Omega, \\
  \uu - \uu_\infty &\to \mathbf{0}, && |\xx| \to \infty,
\end{alignat}
%
where $\uu$ is the velocity, $p$ is the
pressure, $\uu_\infty$ is the background flow, and $\mu$ is the constant viscosity. 
%
Since each particle $\Gamma_i$ with centre $\aa_i$ is a rigid body, its velocity satisfies 
\ReviewerOne{the no-slip boundary condition}
\begin{align}
\label{eq:rigid_bc}
  \ReviewerOne{\uu}(\xx) = \vv_i + \omega_i (\xx - \aa_i)^\perp, \quad 
    \xx \in \Gamma_i,
\end{align}
where $\vv_i$ is its translational velocity and $\omega_i$ is its
angular velocity. Here, $\langle x, y \rangle^{\perp} = \langle -y, x
\rangle$.
%Therefore, the no-slip boundary condition on each particle is
%
%
%\begin{align}
%\label{eq:rigid_bc}
%  \uu(\xx) = \vv_i + \omega_i (\xx - \aa_i)^\perp, \quad
%    \xx \in \Gamma_i.
%\end{align}
%
%
To determine the translational and angular velocities of each particle,
we define imposed forces $\FF_i$ and torques $T_i$ acting on each
particle. Since the small particles are inertialess, force and torque
balance gives 
\begin{alignat}{2}
  \label{eq:force}
  \FF_i &- \int_{\Gamma_i} \ssigma \cdot \nnu \, \dif s = \mathbf{0},
  && i=1,\ldots,N_b,\\
  \label{eq:torque}
  T_i &- \int_{\Gamma_i} (\xx - \aa_i)^\perp \cdot 
    (\ssigma \cdot \nnu) \, \dif s = 0, \qquad && i=1,\ldots,N_b,
\end{alignat}
where $\ssigma = -p \mathbf{I} + \mu \left(\nabla \uu + \nabla \uu^T
\right)$ is the hydrodynamic stress tensor (pressure tensor) and
$\nnu$ is the particle outward normal. The process of finding the
translational and angular velocities given the forces and torques is
referred to as the mobility problem.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Imposed Forces}
The imposed forces and torques contain two parts: hydrophobic attraction
and repulsion. The hydrophobic attraction potential was introduced
by~\cite{Fu20} and is responsible for forming particle aggregates that
sequester their hydrophobic surface regions (Figure \ref{fig:figure0}b).
We model hydrophobic attraction by solving the screened Laplace equation
boundary value problem
\begin{alignat}{2}
  \label{eq:SL}
-\rho^2 \Delta \ReviewerTwo{\eta} + \ReviewerTwo{\eta} &=0,            && \xx \in \Omega,\\
\label{eq:SLbc}
\ReviewerTwo{\eta}(\xx) &= f_i(\xx),\qquad  && \xx \in \Gamma_i,\; i=1,\ldots,N_b, \\
\label{eq:SLff}
\ReviewerTwo{\eta} &\to 0,                          &&|\xx| \to \infty,
\end{alignat}
where $0 \leq f_i \leq 1$ is a material label with $f_i = 0$,
respectively $1$, representing hydrophilic, respectively hydrophobic,
portions of the surface. We assume that both $f_i$ and $\Gamma_i$ are
smooth. The parameter $\rho > 0$ is the decay length of attraction. The
forces and torques of attraction are 
\begin{align}
  \label{eq:hydrophobicAttraction}
  \FF_i^{\text{hydro}} = \int_{\Gamma_i} {\bf T}\cdot \nnu \, \dif s, 
    \quad 
  T_i^{\text{hydro}} = \int_{\Gamma_i} (\xx - \aa_i)^{\perp} \cdot ({\bf T} \cdot \nnu) \dif s,
\end{align}
where
\begin{align}
  \label{eq:stress}
\mathbf{T}
= \gamma\rho^{-1}\ReviewerTwo{\eta}^2 \mathbf{I} + 2\rho\gamma \left(\tfrac{1}{2}|\nabla
  \ReviewerTwo{\eta}|^2 \mathbf{I} - \nabla \ReviewerTwo{\eta}  \nabla \ReviewerTwo{\eta}^T\right)
\end{align}
is the hydrophobic stress tensor and $\gamma > 0$ is
the interfacial
tension.

@@

\ReviewerThree{
The high-order interpolation-based quadrature rule used to compute the
nearly-singular integrals has been shown to accurately capture the
lubrication hydrodynamics in the narrow space between boundaries when
the repulsive potential $P$ gives a large steric
force~\citep{qua-bir2014}. In the simulations we adjust the spatial
resolution on the particle boundary to ensure that the lubrication
hydrodynamics is well resolved as in~\citep{qua-vee-you2019,
qua-gan-you2021}.
}
%

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Integral Equation Method}
\label{sec:IEM}
Computing the hydrophobic attraction potential and the particle forces
and torques requires the solution of elliptic partial differential
equations (PDEs) in an unbounded complex domain. We recast both these
PDEs as boundary integral equations (BIEs). We discretize each BIE at
$N$ points on each of the $N_b$ particles with a collocation method.
\ReviewerOne{All derivatives are computed with spectrally-accurate
Fourier differentiation.} Integrals that are smooth are computed with
the spectrally-accurate trapezoid rule, and nearly-singular integrals,
caused by close contact between two particles, are computed with a
high-order interpolation-based quadrature rule (\cite{qua-bir2014}).
After discretizing and applying quadrature, the resulting linear system
is solved with matrix-free GMRES, and we guarantee that the number of
GMRES iterations is mesh-independent by using second-kind BIEs.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{HAP Boundary Integral Equation}
Similar to our previous work (\cite{Fu20}), we represent the
\ReviewerTwo{hydrophobic attraction potential (HAP)} as a double-layer
potential
\begin{align}
  \label{eq:HAP_DLP}
  \ReviewerTwo{\eta}(\xx) = \frac{1}{2\pi} \int_{\bd\Omega} \left(\pderiv{}{\nnu_\yy}
    K_0 \left(\frac{|\xx - \yy|}{\rho}\right)\right) 
    \sigma(\yy) \, \dif s_\yy, \quad \xx \in \Omega,
\end{align}
where $K_0$ is the zeroth-order modified Bessel function of the first
kind and the integral is taken in the sense of principle value whenever
$\xx \in \partial \Omega$.  By requiring that the density function
$\sigma$ satisfies the second-kind integral equation
\begin{equation}
\label{eq:screenedSKIE}
  f(\xx) = \frac{1}{2}\sigma(\xx) + 
    \frac{1}{2\pi}\int_{\bd\Omega} \left(\pderiv{}{\nnu_\yy}
    K_0 \left(\frac{|\xx - \yy|}{\rho}\right)\right) \sigma(\yy) \, 
    \dif s_\yy, \quad \xx \in \bd\Omega,
\end{equation}
the HAP double-layer potential~\eqref{eq:HAP_DLP} satisfies the screened
Laplace equation~\eqref{eq:SL}--\eqref{eq:SLff}. After
discretizing~\eqref{eq:screenedSKIE}, the result is an $NN_b \times
NN_b$ linear system that is solved with block-diagonal preconditioned
GMRES.

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Main Theoretical Result: Calculating the Hydrophobic Force}
\label{subsec:calculating_force}
Once \eqref{eq:screenedSKIE} has been solved for $\sigma$, we need to
evaluate the integrals~\eqref{eq:hydrophobicAttraction} which are the
HAP forces and torques. These integrals involve the
stress~\eqref{eq:stress} which contains a singular integral for the
gradient of the double-layer potential. To avoid singular integrals, we
first define
\begin{align}
  \label{eq:uidef}
  w_i(\xx) = \ReviewerTwo{\eta}(\xx) - \ReviewerTwo{\eta}_i(\xx),
\end{align}
where
\begin{align}
  \ReviewerTwo{\eta}_i(\xx) &= \frac{1}{2\pi} \int_{\Gamma_i} \left(\pderiv{}{\nnu_\yy}
    K_0 \left(\frac{|\xx - \yy|}{\rho}\right)\right) 
    \sigma(\yy) \, \dif s_\yy, \quad \xx \in \mathbb{R}^2.
\end{align}
That is, $w_i(\xx)$ is the double-layer potential~\eqref{eq:HAP_DLP}
with $\Gamma_i$ excluded from $\bd\Omega$. Having defined $w_i$, we prove
\begin{theorem}
\begin{align}
  \label{eq:recipforcetorque}
  \FF_i^{\mathrm{hydro}} = \int_{\Gamma_i} \JJ_i \,\dif s,\quad
  T_i^{\mathrm{hydro}}    = \int_{\Gamma_i} 
    (\xx - \aa_i)^{\perp} \cdot \JJ_i  \,\dif s,
\end{align}
where
\begin{align}
  \label{eq:jumpstress1}
  \JJ_{i} = 2\gamma\rho^{-1} \sigma w_i \nnu + 
    2\gamma\rho \frac{d\sigma}{ds} \frac{dw_i}{ds} \nnu -
    2\gamma\rho \frac{d\sigma}{ds} \frac{dw_i}{d\nnu} \ttau.
\end{align}
\end{theorem}
The symbols $\ttau$ and $\frac{d}{ds}$ are the unit tangent and arc
length derivative for $\Gamma_i$, respectively (Figure
\ref{fig:figure0}a.) The result is valid for any smooth particle shape
or boundary condition. The advantage of
using~\eqref{eq:recipforcetorque} over
using~\eqref{eq:hydrophobicAttraction} is that the components $\sigma$,
$w_i$, $\frac{d\sigma}{ds}$, and $\frac{dw_i}{ds}$ of $\JJ_i$ are smooth
functions, whereas the components of \eqref{eq:stress} are singular
integrals.

@@

To prove \eqref{eq:recipforcetorque}, let 
\begin{align*}
  {\bf T} &=
    \SS(\ReviewerTwo{\eta}_i,\ReviewerTwo{\eta}_i) +(\SS(\ReviewerTwo{\eta}_i,w_i) +\SS(w_i,\ReviewerTwo{\eta}_i)) +\SS(w_i,w_i) \\
  &= {\bf T}_1 + {\bf T}_2 + {\bf T}_3
\end{align*}
where we introduce the bilinear form
\begin{equation}
\label{eq:Tsplit}
\SS(\ReviewerTwo{\eta},v)
=  \gamma\rho^{-1} \ReviewerTwo{\eta}v {\bf I} + \gamma\rho \nabla \ReviewerTwo{\eta} \cdot \nabla v {\bf I} - 2 \gamma \rho \nabla \ReviewerTwo{\eta} \nabla v^T.
\end{equation}
Using the fact that $\ReviewerTwo{\eta}$,  $\ReviewerTwo{\eta}_i$, and $w_i$ solve the screened Laplace
equation~\eqref{eq:SL}, and that $\mathbf{T}$, $\mathbf{T}_j$, $j = 1,
2, 3$ are symmetric, it is straightforward to verify that 
  \begin{equation}
    \label{eq:decompdivfree}
    \nabla \cdot {\bf T}_j = 0, \quad
    \nabla \cdot ((\xx-\aa_i)^{\perp} \cdot {\bf T}_j) = 0, \quad j = 1, 2, 3.
  \end{equation}

@@

Let $U_i$ be the interior of the particle indexed by $i$. For $\xx_0
\in \Gamma_i$ and an arbitrary function $g(\xx)$, the notation
\begin{align}
  \jump{g}(\xx_0) = \lim_{\substack{\xx \to \xx_0 \\ \xx \in U_i^c}}g(\xx)  - 
                    \lim_{\substack{\xx \to \xx_0 \\ \xx \in U_i}}g(\xx),
\end{align}
denotes the jump of the limits of $g(\xx)$ taken from the outside to
the inside of $\Gamma_i$.
%\begin{align}
%\lim_{\xx \to \xx_0^+}g(\xx),\quad 
%\lim_{\xx \to \xx_0^-}g(\xx), \quad
%  \jump{g}(\xx_0) = \lim_{\xx \to \xx_0^+}g(\xx)  - \lim_{\xx \to \xx_0^-}g(\xx)
%\end{align}
%denotes the limit taken from points in $U_i^c$,  the limit taken from
%points in $U_i$, and the jump, respectively.  
\begin{lemma}
\begin{align}
  \label{eq:prejump}
  \FF_i^{\mathrm{hydro}} = \int_{\Gamma_i} \jump{{\bf T}_2 \cdot \nnu}  \, \dif s,\quad
  T_i^{\mathrm{hydro}} = \int_{\Gamma_i} (\xx - \aa_i)^{\perp} \cdot
  \jump{{\bf T}_2 \cdot \nnu} \, \dif s.
\end{align}
\end{lemma}
\begin{proof}
To show~\eqref{eq:prejump}, we expand \eqref{eq:hydrophobicAttraction} as
\begin{align}
  \FF_i = \int_{\Gamma_i} \left({\bf T}_1 \cdot \nnu + 
    {\bf T}_2 \cdot \nnu + {\bf T}_3 \cdot \nnu \right) \,\dif s.
\end{align}
By~\eqref{eq:uidef} and~\eqref{eq:decompdivfree}, we have that $u_i$ is
smooth and $\nabla \cdot {\bf T}_1 = \mathbf{0}$ in $\mathbb{R}^n
\setminus U_i$. Similarly, $w_i = \ReviewerTwo{\eta} - \ReviewerTwo{\eta}_i$ is smooth and $\nabla \cdot
{\bf T}_3 = \mathbf{0}$ in $U_i$. By the divergence theorem,  
\begin{align}
  \int_{\Gamma_i}  {\bf T}_1 \cdot \nnu \,\dif s
  = -\int_{\mathbb{R}^n \setminus U_i} \nabla \cdot {\bf T}_1 \,\dif \xx = \mathbf{0},\quad
    \int_{\Gamma_i}  {\bf T}_3 \cdot \nnu\,\dif s
  = \int_{U_i} \nabla \cdot {\bf T}_3 \,\dif \xx = \mathbf{0}.
\end{align}
Finally, $u_i$ and $w_i$ are smooth and $\nabla \cdot {\bf T}_2= 0$ in $U_i$. This gives
\begin{align}
  \mathbf{0} = \int_{U_i} \nabla \cdot {\bf T}_2 \, \dif \xx = \int_{\Gamma_i}  
    ({\bf T}_2 \cdot \nnu)^-\,\dif s,
\end{align}
where the superscript denotes the limit taken from in $U_i$.  
Combining the above gives the first equation in \eqref{eq:prejump}.
The derivation for the second equation in \eqref{eq:prejump} is identical. 
\end{proof}

>>>>

\begin{figure}
\begin{center}
\includegraphics[width=\textwidth]{fig1.eps}
\end{center}
\caption{Panel (a) illustrates the domain and boundary conditions for
  the mobility problem. The color map in panels (b)--(e) is the solution
  $u$ of \eqref{eq:SL}. Red is for $\eta  = 1$ and blue is for $\eta  = 0$.
  Particles self-assemble into vesicle bilayers (panel (b)) and
  eventually arrange along inner and outer leaflets. In panel (c), $C_M$
  is the midplane curve, and $A$ is the enclosed area.
  %, and $L$ is the arc length. 
  Initially stretched vesicles relax to equilibrium with fluid
  flow across the bilayer. The study considers a single vesicle in
  background flows such as shear flow (panel (d)) and hydrodynamic
  vesicle-vesicle interactions (panel (e)).}
\label{fig:figure0}
\end{figure}

@@

In the present work, we extend the hybrid continuum model in~\cite{Fu20}
for the Janus suspension to incorporate the collective hydrodynamics of
a Janus suspension under various flows. The JP vesicles in our
simulations replicate well-known vesicle hydrodynamics
such as tank-treading and inter-leaflet slippage in a shear flow and
migration in Poiseuille flow from continuum models. Furthermore we use
the hybrid continuum model to investigate permeability and rupture of a
bilayer membrane due to an imposed flow.  Finally, we compare a pair of
interacting JP vesicles with a continuum model of a pair of vesicles.

@@

To simulate the hydrodynamics of Janus particles in Stokes flow,
we require a numerical method to avoid unphysical contact between rigid
Janus particles. Optimization-based contact methods introduce
constraints, such as enforcing a non-positive space-time interference
volume (\cite{lu-rah-zor2017, Lukas19, yan-cor-mal-vee-she2020}). These
methods do not introduce stiffness, but do require solving potentially
expensive nonlinear complementarity problems at each time step.
Repulsion-based contact methods, which we employ, introduce an
artificial repulsion force that increases in strength as two particles
approach one another (\cite{glo-pan-hes-jos-per2001, fen-mic2004,
kab-qua-bir2018}). Strong repulsion forces can introduce numerical
stiffness, but with the presence of the hydrophobic forces, we maintain
contact-free suspensions with a relatively soft repulsive
force (compared to the short-range repulsion that diverges in the Lennard-Jones potential).

@@

\section{Governing Equations\label{sec:governing_eqs}}
\subsection{\label{mobility}Mobility Problem}
The objective of this work is to study the hydrodynamics of JP vesicles
in background flows. We consider an $N_b$-many body collection of JP
suspended in a two-dimensional unbounded domain $\Omega$. The boundary
of each particle is denoted by $\Gamma_i$ so that $\bd \Omega = \Gamma_1
\cup \Gamma_2 \cup \cdots \cup \Gamma_{N_b}$ (Figure
\ref{fig:figure0}a). Assuming the inertial terms are negligible, the
governing equations are
\begin{alignat}{3}
\label{eq:stokes}
  -\mu \Delta \uu + \nabla p &= \mathbf{0}, 
    && \xx \in \Omega, \\
  \nabla\cdot \uu &= 0, \qquad && \xx \in \Omega, \\
  \uu - \uu_\infty &\to \mathbf{0}, && |\xx| \to \infty,
\end{alignat}
%
where $\uu$ is the velocity, $p$ is the
pressure, $\uu_\infty$ is the background flow, and $\mu$ is the constant viscosity. 
%
Since each particle $\Gamma_i$ with centre $\aa_i$ is a rigid body, its velocity satisfies 
the no-slip boundary condition
\begin{align}
\label{eq:rigid_bc}
  \uu(\xx) = \vv_i + \omega_i (\xx - \aa_i)^\perp, \quad 
    \xx \in \Gamma_i,
\end{align}
where $\vv_i$ is its translational velocity and $\omega_i$ is its
angular velocity. Here, $\langle x, y \rangle^{\perp} = \langle -y, x
\rangle$.
%Therefore, the no-slip boundary condition on each particle is
%
%
%\begin{align}
%\label{eq:rigid_bc}
%  \uu(\xx) = \vv_i + \omega_i (\xx - \aa_i)^\perp, \quad
%    \xx \in \Gamma_i.
%\end{align}
%
%
To determine the translational and angular velocities of each particle,
we define imposed forces $\FF_i$ and torques $T_i$ acting on each
particle. Since the small particles are inertialess, force and torque
balance gives 
\begin{alignat}{2}
  \label{eq:force}
  \FF_i &- \int_{\Gamma_i} \ssigma \cdot \nnu \, \dif s = \mathbf{0},
  && i=1,\ldots,N_b,\\
  \label{eq:torque}
  T_i &- \int_{\Gamma_i} (\xx - \aa_i)^\perp \cdot 
    (\ssigma \cdot \nnu) \, \dif s = 0, \qquad && i=1,\ldots,N_b,
\end{alignat}
where $\ssigma = -p \mathbf{I} + \mu \left(\nabla \uu + \nabla \uu^T
\right)$ is the hydrodynamic stress tensor (pressure tensor) and
$\nnu$ is the particle outward normal. The process of finding the
translational and angular velocities given the forces and torques is
referred to as the mobility problem.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Imposed Forces}
The imposed forces and torques contain two parts: hydrophobic attraction
and repulsion. The hydrophobic attraction potential was introduced
by~\cite{Fu20} and is responsible for forming particle aggregates that
sequester their hydrophobic surface regions (Figure \ref{fig:figure0}b).
We model hydrophobic attraction by solving the screened Laplace equation
boundary value problem
\begin{alignat}{2}
  \label{eq:SL}
-\rho^2 \Delta \eta  + \eta  &=0,            && \xx \in \Omega,\\
\label{eq:SLbc}
\eta (\xx) &= f_i(\xx),\qquad  && \xx \in \Gamma_i,\; i=1,\ldots,N_b, \\
\label{eq:SLff}
\eta  &\to 0,                          &&|\xx| \to \infty,
\end{alignat}
where $0 \leq f_i \leq 1$ is a material label with $f_i = 0$,
respectively $1$, representing hydrophilic, respectively hydrophobic,
portions of the surface. We assume that both $f_i$ and $\Gamma_i$ are
smooth. The parameter $\rho > 0$ is the decay length of attraction. The
forces and torques of attraction are 
\begin{align}
  \label{eq:hydrophobicAttraction}
  \FF_i^{\text{hydro}} = \int_{\Gamma_i} {\bf T}\cdot \nnu \, \dif s, 
    \quad 
  T_i^{\text{hydro}} = \int_{\Gamma_i} (\xx - \aa_i)^{\perp} \cdot ({\bf T} \cdot \nnu) \dif s,
\end{align}
where
\begin{align}
  \label{eq:stress}
\mathbf{T}
= \gamma\rho^{-1}\eta ^2 \mathbf{I} + 2\rho\gamma \left(\tfrac{1}{2}|\nabla
  \eta |^2 \mathbf{I} - \nabla \eta   \nabla \eta ^T\right)
\end{align}
is the hydrophobic stress tensor and $\gamma > 0$ is
the interfacial
tension.

@@

The high-order interpolation-based quadrature rule used to compute the
nearly-singular integrals has been shown to accurately capture the
lubrication hydrodynamics in the narrow space between boundaries when
the repulsive potential $P$ gives a large steric
force~\citep{qua-bir2014}. In the simulations we adjust the spatial
resolution on the particle boundary to ensure that the lubrication
hydrodynamics is well resolved as in~\citep{qua-vee-you2019,
qua-gan-you2021}.

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Integral Equation Method}
\label{sec:IEM}
Computing the hydrophobic attraction potential and the particle forces
and torques requires the solution of elliptic partial differential
equations (PDEs) in an unbounded complex domain. We recast both these
PDEs as boundary integral equations (BIEs). We discretize each BIE at
$N$ points on each of the $N_b$ particles with a collocation method.
All derivatives are computed with spectrally-accurate
Fourier differentiation. Integrals that are smooth are computed with
the spectrally-accurate trapezoid rule, and nearly-singular integrals,
caused by close contact between two particles, are computed with a
high-order interpolation-based quadrature rule (\cite{qua-bir2014}).
After discretizing and applying quadrature, the resulting linear system
is solved with matrix-free GMRES, and we guarantee that the number of
GMRES iterations is mesh-independent by using second-kind BIEs.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{HAP Boundary Integral Equation}
Similar to our previous work (\cite{Fu20}), we represent the
hydrophobic attraction potential (HAP) as a double-layer
potential
\begin{align}
  \label{eq:HAP_DLP}
  \eta (\xx) = \frac{1}{2\pi} \int_{\bd\Omega} \left(\pderiv{}{\nnu_\yy}
    K_0 \left(\frac{|\xx - \yy|}{\rho}\right)\right) 
    \sigma(\yy) \, \dif s_\yy, \quad \xx \in \Omega,
\end{align}
where $K_0$ is the zeroth-order modified Bessel function of the first
kind and the integral is taken in the sense of principle value whenever
$\xx \in \partial \Omega$.  By requiring that the density function
$\sigma$ satisfies the second-kind integral equation
\begin{equation}
\label{eq:screenedSKIE}
  f(\xx) = \frac{1}{2}\sigma(\xx) + 
    \frac{1}{2\pi}\int_{\bd\Omega} \left(\pderiv{}{\nnu_\yy}
    K_0 \left(\frac{|\xx - \yy|}{\rho}\right)\right) \sigma(\yy) \, 
    \dif s_\yy, \quad \xx \in \bd\Omega,
\end{equation}
the HAP double-layer potential~\eqref{eq:HAP_DLP} satisfies the screened
Laplace equation~\eqref{eq:SL}--\eqref{eq:SLff}. After
discretizing~\eqref{eq:screenedSKIE}, the result is an $NN_b \times
NN_b$ linear system that is solved with block-diagonal preconditioned
GMRES.

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Main Theoretical Result: Calculating the Hydrophobic Force}
\label{subsec:calculating_force}
Once \eqref{eq:screenedSKIE} has been solved for $\sigma$, we need to
evaluate the integrals~\eqref{eq:hydrophobicAttraction} which are the
HAP forces and torques. These integrals involve the
stress~\eqref{eq:stress} which contains a singular integral for the
gradient of the double-layer potential. To avoid singular integrals, we
first define
\begin{align}
  \label{eq:uidef}
  w_i(\xx) = \eta (\xx) - \eta _i(\xx),
\end{align}
where
\begin{align}
  \eta _i(\xx) &= \frac{1}{2\pi} \int_{\Gamma_i} \left(\pderiv{}{\nnu_\yy}
    K_0 \left(\frac{|\xx - \yy|}{\rho}\right)\right) 
    \sigma(\yy) \, \dif s_\yy, \quad \xx \in \mathbb{R}^2.
\end{align}
That is, $w_i(\xx)$ is the double-layer potential~\eqref{eq:HAP_DLP}
with $\Gamma_i$ excluded from $\bd\Omega$. Having defined $w_i$, we prove
\begin{theorem}
\begin{align}
  \label{eq:recipforcetorque}
  \FF_i^{\mathrm{hydro}} = \int_{\Gamma_i} \JJ_i \,\dif s,\quad
  T_i^{\mathrm{hydro}}    = \int_{\Gamma_i} 
    (\xx - \aa_i)^{\perp} \cdot \JJ_i  \,\dif s,
\end{align}
where
\begin{align}
  \label{eq:jumpstress1}
  \JJ_{i} = 2\gamma\rho^{-1} \sigma w_i \nnu + 
    2\gamma\rho \frac{d\sigma}{ds} \frac{dw_i}{ds} \nnu -
    2\gamma\rho \frac{d\sigma}{ds} \frac{dw_i}{d\nnu} \ttau.
\end{align}
\end{theorem}
The symbols $\ttau$ and $\frac{d}{ds}$ are the unit tangent and arc
length derivative for $\Gamma_i$, respectively (Figure
\ref{fig:figure0}a.) The result is valid for any smooth particle shape
or boundary condition. The advantage of
using~\eqref{eq:recipforcetorque} over
using~\eqref{eq:hydrophobicAttraction} is that the components $\sigma$,
$w_i$, $\frac{d\sigma}{ds}$, and $\frac{dw_i}{ds}$ of $\JJ_i$ are smooth
functions, whereas the components of \eqref{eq:stress} are singular
integrals.

@@

To prove \eqref{eq:recipforcetorque}, let 
\begin{align*}
  {\bf T} &=
    \SS(\eta _i,\eta _i) +(\SS(\eta _i,w_i) +\SS(w_i,\eta _i)) +\SS(w_i,w_i) \\
  &= {\bf T}_1 + {\bf T}_2 + {\bf T}_3
\end{align*}
where we introduce the bilinear form
\begin{equation}
\label{eq:Tsplit}
\SS(\eta ,v)
=  \gamma\rho^{-1} \eta v {\bf I} + \gamma\rho \nabla \eta  \cdot \nabla v {\bf I} - 2 \gamma \rho \nabla \eta  \nabla v^T.
\end{equation}
Using the fact that $\eta $,  $\eta _i$, and $w_i$ solve the screened Laplace
equation~\eqref{eq:SL}, and that $\mathbf{T}$, $\mathbf{T}_j$, $j = 1,
2, 3$ are symmetric, it is straightforward to verify that 
  \begin{equation}
    \label{eq:decompdivfree}
    \nabla \cdot {\bf T}_j = 0, \quad
    \nabla \cdot ((\xx-\aa_i)^{\perp} \cdot {\bf T}_j) = 0, \quad j = 1, 2, 3.
  \end{equation}

@@

Let $U_i$ be the interior of the particle indexed by $i$. For $\xx_0
\in \Gamma_i$ and an arbitrary function $g(\xx)$, the notation
\begin{align}
  \jump{g}(\xx_0) = \lim_{\substack{\xx \to \xx_0 \\ \xx \in U_i^c}}g(\xx)  - 
                    \lim_{\substack{\xx \to \xx_0 \\ \xx \in U_i}}g(\xx),
\end{align}
denotes the jump of the limits of $g(\xx)$ taken from the outside to
the inside of $\Gamma_i$.
%\begin{align}
%\lim_{\xx \to \xx_0^+}g(\xx),\quad 
%\lim_{\xx \to \xx_0^-}g(\xx), \quad
%  \jump{g}(\xx_0) = \lim_{\xx \to \xx_0^+}g(\xx)  - \lim_{\xx \to \xx_0^-}g(\xx)
%\end{align}
%denotes the limit taken from points in $U_i^c$,  the limit taken from
%points in $U_i$, and the jump, respectively.  
\begin{lemma}
\begin{align}
  \label{eq:prejump}
  \FF_i^{\mathrm{hydro}} = \int_{\Gamma_i} \jump{{\bf T}_2 \cdot \nnu}  \, \dif s,\quad
  T_i^{\mathrm{hydro}} = \int_{\Gamma_i} (\xx - \aa_i)^{\perp} \cdot
  \jump{{\bf T}_2 \cdot \nnu} \, \dif s.
\end{align}
\end{lemma}
\begin{proof}
To show~\eqref{eq:prejump}, we expand \eqref{eq:hydrophobicAttraction} as
\begin{align}
  \FF_i = \int_{\Gamma_i} \left({\bf T}_1 \cdot \nnu + 
    {\bf T}_2 \cdot \nnu + {\bf T}_3 \cdot \nnu \right) \,\dif s.
\end{align}
By~\eqref{eq:uidef} and~\eqref{eq:decompdivfree}, we have that $u_i$ is
smooth and $\nabla \cdot {\bf T}_1 = \mathbf{0}$ in $\mathbb{R}^n
\setminus U_i$. Similarly, $w_i = \eta  - \eta _i$ is smooth and $\nabla \cdot
{\bf T}_3 = \mathbf{0}$ in $U_i$. By the divergence theorem,  
\begin{align}
  \int_{\Gamma_i}  {\bf T}_1 \cdot \nnu \,\dif s
  = -\int_{\mathbb{R}^n \setminus U_i} \nabla \cdot {\bf T}_1 \,\dif \xx = \mathbf{0},\quad
    \int_{\Gamma_i}  {\bf T}_3 \cdot \nnu\,\dif s
  = \int_{U_i} \nabla \cdot {\bf T}_3 \,\dif \xx = \mathbf{0}.
\end{align}
Finally, $u_i$ and $w_i$ are smooth and $\nabla \cdot {\bf T}_2= 0$ in $U_i$. This gives
\begin{align}
  \mathbf{0} = \int_{U_i} \nabla \cdot {\bf T}_2 \, \dif \xx = \int_{\Gamma_i}  
    ({\bf T}_2 \cdot \nnu)^-\,\dif s,
\end{align}
where the superscript denotes the limit taken from in $U_i$.  
Combining the above gives the first equation in \eqref{eq:prejump}.
The derivation for the second equation in \eqref{eq:prejump} is identical. 
\end{proof}
